Reference label transfer from the fetal full reference (Cao et al.) for `r params$sample_id`

### 2024-08-28 analyses/cell-type-wilms-tumor-06/notebook_template/02a_label-transfer_fetal_full_reference_Cao.Rmd
few changes/typos PR #706
Update 02a_label-transfer_fetal_full_reference_Cao.Rmd

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
options(future.globals.maxSize= 8912896000000)
s <- RunAzimuth(srat, reference ="fetusref" )

@@

```{r save}
saveRDS(object = srat, file = file.path(output_dir, paste0("00a-fetal_full_label-transfer_",params$sample_id,".Rds")))
```

>>>>

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
options(future.globals.maxSize= 891289600000000)
s <- RunAzimuth(srat, reference ="fetusref", k.weight = 30 )

@@

```{r save}
saveRDS(object = srat, file = file.path(output_dir, paste0("02a-fetal_full_label-transfer_",params$sample_id,".Rds")))
```
